\documentclass[11pt]{article}

\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65em}
\pagenumbering{gobble}

\begin{document}

{\Large \textbf{Derek Martin}}\\
Mechanical Engineering | Physics Minor | Aerospace Focus\\
\href{mailto:derrickmartin3737@gmail.com}{derrickmartin3737@gmail.com}

\vspace{1.1em}

April 30, 2026

Evensol Hiring Team\\
Evensol LLC\\
Sisters, Oregon

\vspace{1.1em}

Dear Evensol Hiring Team,

I am a mechanical engineering student at Oregon State University with a physics minor, an aerospace focus, and prior internship experience with Evensol. I am interested in returning to Evensol in a mechanical engineering capacity because the work connects practical engineering, renewable energy, field reliability, and careful project execution. My previous experience with Evensol gave me a direct look at the level of technical detail required to support renewable fuels projects, and it strengthened my interest in contributing to biogas and renewable natural gas systems.

During my internship, I supported engineering work through equipment inspections, troubleshooting, preventative maintenance, feasibility study support, cost estimating, and data organization. I used spreadsheets to track information, support analysis, and communicate findings in a way that could help project decisions. That experience was valuable because it showed me how mechanical engineering work fits into a larger operating environment where design choices, maintenance practices, documentation, and communication all affect reliability.

I also bring design and technical skills that would help me contribute to Evensol's project and operations work. I have used Autodesk Fusion 360 to model and analyze mechanical components, including a high-safety-factor winch stand designed to lift a 150 lb motor and a custom hand crank. In addition, I have developed Python automation and control software as part of my engineering coursework and capstone work. These experiences have helped me become comfortable moving between hands-on mechanical problems, digital modeling, and structured technical documentation.

My background outside the classroom has also shaped the way I work. As a former wildland firefighter and EMT, I learned to communicate clearly, follow safety procedures, stay dependable under pressure, and work as part of a team when conditions are demanding. Those habits translate directly to engineering environments where safety, reliability, and accountability matter. I would be excited to bring that mindset back to Evensol while continuing to grow as a mechanical engineer.

Thank you for considering my application. I would appreciate the opportunity to discuss how my prior Evensol experience, mechanical design skills, and interest in renewable energy systems could support your team.

\vspace{0.8em}

Sincerely,\\
Derek Martin

\end{document}
